{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2015-01-28 brains-protocol.tex
Note that each feature encodes a different number of words

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.

>>>>

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.\footnote{Note that since the final features stem from different datasets, they do not encode the same amounts of words (and \emph{a fortiori}, not always the same words). Thus, frequency encodes about 22.6k words, age of acquisition 30.1k words, number of phonemes 123.4k words, number of synonyms 111.2k, and clustering coefficient 5.7k words (because of the relatively small size of the Free Association dataset). This is not a problem since the analysis is done on a per-feature basis, with no need for words to be encoded in all the features at once.}
